The limits of self commitment and private paternalism \thanks{}

### 2021-10-22 donde.tex
benefit_vs_choice analysis & corrections in causal forests
Former-commit-id: a94e41dada3d0ce771362fc224735b66a8842aa5

    \end{center}
        \scriptsize
        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract. To do this we proceed in two steps. First, we estimate treatment effects in the forcing arm by comparing the fee-forcing arm against the status quo arm. We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests. Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s. Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan. $z$\% is a level of tolerance we can vary and we plot it in the X-axis. The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''. We use bootstrap to tighten the confidence intervals (CIs). \cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal. We compute the HTE ($\mu$) together with standard errors ($\sigma$) . For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) . This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI. Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident. Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the fee-choice arm into the fee-commitment contract. Panel (d) asks whether it is the case that people with larger causal savings from the fee-forcing contract would be more likely to select that contract. To do this we proceed in two steps as well. First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the fee-forcing contract for a client with characteristics $x_i$. We extrapolate this model to clients in the fee-forcing arm to estimate what would they have chosen if we had given them choice. Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins. The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin. Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are more likely to choose it.  Using all bins we estimate a slope of zero in the relationship. Using the 80 right most points, we estimate a \textit{positive} relationship.
        %\textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
\end{figure}

>>>>

    \end{center}
        \scriptsize
        In Panel (a) we estimate what the treatment effect of the commitment contract \textit{would have been} for all subjects in the choice arm if they had been forced into the fee-commitment contract. To do this we proceed in two steps. First, we estimate treatment effects in the forcing arm by comparing the fee-forcing arm against the status quo arm. We let these effects be heterogeneous as a function of our $x$'s using \cite{atheygrf}'s methodology of causal forests. Second, we extrapolate these treatment effects based on the choice arm using the same $x$'s. Once we have personalized counterfactual treatment effects in the choice arm we calculate what fraction of subjects in the choice arm incurred in financial costs that are  $> z$\% than if they had chosen the opposite contract of what they actually chose, were $z$\% is defined as a fraction of the loan. $z$\% is a level of tolerance we can vary and we plot it in the X-axis. The left Y-axis measures the fraction of subjects that would have been better by a margin of $z$\% if they changed their choice, and the right Y-axis measures the amount of money ``left on the table''. We use bootstrap to tighten the confidence intervals (CIs). \cite{atheygrf}'s heterogeneous treatment effect using GRF is asymptotically normal. We compute the HTE ($\mu$) together with standard errors ($\sigma$) . For every pledge, we draw a random effect from a normal distribution with parameters ($\mu$,$\sigma^2$), and compute via bootstrap the percentage that choose wrong, along normal-approximation CIs (results are robust if we use instead percentile CIs or bias-corrected CIs) . This allows us to estimate a distribution for the upper and lower bound CIs, which we then use to obtain a 95\% CI. Panel (b) is analogous to Panel (a) except that it does the exercise separately for clients we classified as overconfident ($OC_i:=\mathbbm{1}(P^s_i-\widehat{P_i(X_i)}>0))$ and those we classified as not overconfident. Panel (c) simulates what percentage would be better by at least $z$ if we forced everybody of those in the fee-choice arm into the fee-commitment contract. Panel (d) asks whether it is the case that people with larger causal benefits from the fee-forcing contract would be more likely to select that contract. To do this we proceed in two steps as well. First we estimate a flexible model of take-up of the fee commitment contract \textit{in the choice arm} using random forests, and from this model obtain a probability $P(x_i)$ of choosing the fee-forcing contract for a client with characteristics $x_i$. We extrapolate this model to clients in the fee-forcing arm to estimate what would they have chosen if we had given them choice. Figure (d) plots $\widehat{P(x_i)}$ in the X-axis using a binscatter that splits the X-axis in 100 percentile bins. The Y-axis plots the heterogeneous treatment effects of the fee forcing contract on the probability of losing the pawns (more negative means then more likely to recover it), averaged for the respective x-axis bin. Positive assortative selection would mean a negative relationship: those who benefit more by treatment and lose the pawn less are \emph{less} likely to choose it.  Using all bins we estimate a slope of zero in the relationship. Using the 80 right most points, we estimate a \textit{positive} relationship.
        %\textit{Do file: }  \texttt{effect\_contr\_takeup.do, choose\_wrong\_quant\_wrong.do, choose\_wrong\_quant\_wrong\_decomposition.do}
\end{figure}
